Inferring the effective start dates of non-pharmaceutical interventions during \covid outbreaks

### 2021-02-08 ms/ms.tex
corrected fixed model conclusions, Re figures

\autoref{fig:Re} demonstrates that estimates from the fixed~$\tau$ model (y-axis) are consistently lower than estimates from the free~$\tau$ model (x-axis), except in Sweden (SE) and Denmark (DK), in which estimation uncertainty is high.
That is, assuming NPIs start at their official date leads to error in the estimation of their impact.
Moreover, these errors increase with the duration of the delay between the official and effective dates (\autoref{fig:Re2}).
These results suggest that the impact of past NPIs is likely to be under-estimated by health officials and researchers if they assume NPIs start at their official dates.
The estimated impact can then be interpreted as ineffectiveness of the NPIs, leading to more aggressive NPIs being applied.

%%% Fig - Re
% generated with
% > source ./Re.sh
% > python Fig_Re.py
\begin{figure}[h]
    \centering
	\includegraphics[width=\textwidth]{../figures/Fig_Re.pdf}
    \caption{
    \textbf{Impact of NPIs is under-estimated when assuming they start at their official date.}
    Shown are estimates of the relative reduction in the effective reproduction number ($R$, see \autoref{eq:Re}), which measures the impact of NPIs on the epidemic.
     The y-axis shows estimates when assuming the start of NPIs is fixed at the official date (fixed~$\tau$). The x-axis shows estimates when inferring the effective start of NPIs from the data (free~$\tau$). The dashed line shows a one-to-one correspondence.
     Markers and bars denote the posterior median and 50\% credible intervals (HDI).
    The relative reductions in $R$ are consistently lower for the fixed~$\tau$ model (below the dashed line), except in Sweden and Denmark in which uncertainty is high.
    \autoref{fig:Re2} shows how the delay in effective start affect the estimation error. 
    AT: Austria, BE: Belgium, CH: Switzerland, CN: Wuhan, China, DE: Germany, DK: Denmark, ES: Spain, FR: France, GB: United Kingdom, IT: Italy, NO: Norway, SE: Sweden.
    } 
    \label{fig:Re}
\end{figure}

>>>>

\autoref{fig:Re} demonstrates that estimates from the fixed~$\tau$ model (y-axis) may be significantly lower than estimates from the free~$\tau$ model (x-axis).
This is the case in six of 12 regions, although the effect size is small in two of these regions (France, FR, and Italy, IT).
Moreover, we find that NPI impact estimation errors increase with the duration of the delay between the official and effective dates (\autoref{fig:Re2}).
These results suggest that the impact of past NPIs can be under-estimated by health officials and researchers if they assume NPIs start at their official dates.
The estimated impact can then be interpreted as ineffectiveness of the NPIs, leading to more aggressive NPIs being applied.

%%% Fig - Re
% generated with
% > source ./Re.sh
% > python Fig_Re.py
\begin{figure}[h]
    \centering
	\includegraphics[width=\textwidth]{../figures/Fig_Re.pdf}
    \caption{
    \textbf{Impact of NPIs is under-estimated when assuming they start at their official date.}
    Shown are estimates of the relative reduction in the effective reproduction number ($R$, see \autoref{eq:Re}), which measures the impact of NPIs on the epidemic.
     The y-axis shows estimates when assuming the start of NPIs is fixed at the official date (fixed~$\tau$). The x-axis shows estimates when inferring the effective start of NPIs from the data (free~$\tau$). The dashed line shows a one-to-one correspondence.
     Markers and bars denote the posterior median and 50\% credible intervals (HDI).
    The relative reductions in $R$ are lower for the fixed~$\tau$ model (below the dashed line) In six of 12 regions.
    \autoref{fig:Re2} shows how the delay in effective start affects the estimation error. 
    AT: Austria, BE: Belgium, CH: Switzerland, CN: Wuhan, China, DE: Germany, DK: Denmark, ES: Spain, FR: France, GB: United Kingdom, IT: Italy, NO: Norway, SE: Sweden.
    } 
    \label{fig:Re}
\end{figure}
